Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-02-16 paper/main.tex
forgot to check in some saved edits

We developed a simple formula (Eqn.~\ref{eqn:prop}) for using a participant's
responses to a small set of multiple-choice questions to estimate how much the
participant ``knows'' about the concept reflected by any arbitrary coordinate,
$x$, in text embedding space (e.g., the content reflected by any moment in a
lecture they had watched; see \nameref{subsec:traces}). Essentially, the
estimated knowledge at the coordinate is given by the weighted average
proportion of quiz questions the participant answered correctly, where the
weights reflect how much each question is ``about'' the content at $x$. When we
apply this approach to estimate the participant's knowledge about the content
presented in each moment of each lecture, we can obtain a detailed timecourse
describing how much ``knowledge'' the participant has about any part of the
lecture. As shown in Figure~\ref{fig:knowledge-timeseries}, we can also apply
this approach separately for the questions from each quiz the participants took
throughout the experiment. From just a few questions per quiz, we obtain a
high-resolution snapshot (at the time each quiz was taken) of what the
participants knew about any moment's content, from either of the two lectures
they watched (comprising a total of 1,100 samples across the two lectures).

>>>>

We developed a simple formula (Eqn.~\ref{eqn:prop}) for using a participant's
responses to a small set of multiple-choice questions to estimate how much the
participant ``knows'' about the concept reflected by any arbitrary coordinate,
$x$, in text embedding space (e.g., the content reflected by any moment in a
lecture they had watched; see \nameref{subsec:traces}). Essentially, the
estimated knowledge at the coordinate is given by the weighted average
proportion of quiz questions the participant answered correctly, where the
weights reflect how much each question is ``about'' the content at $x$. When we
apply this approach to estimate the participant's knowledge about the content
presented in each moment of each lecture, we can obtain a detailed timecourse
describing how much ``knowledge'' the participant has about any part of the
lecture. As shown in Figure~\ref{fig:knowledge-timeseries}, we can also apply
this approach separately for the questions from each quiz the participants took
throughout the experiment. From just a few questions per quiz (see
Sec.~\ref{subsec:traces}), we obtain a high-resolution snapshot (at the time
each quiz was taken) of what the participants knew about any moment's content,
from either of the two lectures they watched (comprising a total of 1,100
samples across the two lectures).
